---
title: "Data Science Homework Intro"
format: html
editor: visual
---

## Questions:

1.  Being a data scientist is about being able to understand and manipulate data while also being able to effectively communicate the story it's telling by doing analysis or modeling.
2.  Data scientists and statisticians are similar in that both work very closely with data. However, there are some key differences such as statisticians working with smaller, clean data while "bringing data to a model." On the other hand data scientists work with larger and messier data where they "bring models to the data."
3.  My background is in statistics, but I am currently perusing a career path in data science working as a product analyst for a home security company. I enjoy looking into the business problem and helping to solve real questions or problems using the (sometimes very messy) data that we have access to from our products.

## R Code:

This code saves an object as 'y' that reports the density of the petal.width column on the iris data set:

```{r}
y <- density(iris$Petal.Width)
y
```

The following code reports the class, type and structure of y:

```{r}
class(y)
typeof(y)
str(y)
```

Here we have hidden the code that produces the following plot:

```{r}
#| echo: false
 plot(y)
```
